The value of being indispensable: a cooperative approach to bargaining with a continuum of players

### 2023-11-20 src/paper/theory.tex
Rewrite abstract and title

\title{The value of intermediation}
\author{Martin Stancsics}

@@

\begin{abstract}
    This paper investigates the idea of using concepts from cooperative game theory (in particular, the Shapley-value) to model bargaining outcomes in games with a few large and a continuum of small players.
    I show that the cooperative approach can be a tractable alternative of explicitly modelling price structures and entry choices in platform settings.
    This approach might be advantageous when one does not want to attribute all the bargaining power to one type of market participants, and at the same time would like to avoid having to deal with an explicit multi-stage bargaining game.
    I demonstrate the advantages of this approach in a stylized model of a vertical market.
\end{abstract}

@@

>>>>

\title{The value of being indispensable: a cooperative approach to bargaining with a continuum of players}
\author{Martin Stancsics}

@@

\begin{abstract}
    This paper investigates the idea of using concepts random order values, a concept from cooperative game theory, to model bargaining outcomes in games with an indispensable player and a continuum of fringe players.
    I show that this approach proves to be very tractable in a number of settings, and leads to results that are in line with one's intuitive expectations about bargaining outcomes.
    Thus, it can be a useful tool in modelling situations where one does not want to attribute all the bargaining power to one type of market participants, and at the same time would like to avoid having to deal with an explicit multi-stage bargaining game.
    On one hand, this paper serves as a taxonomization of various results found in some applied papers.
    Furthermore, it introduces some new results pertaining to the case when participants have different levels of innate bargaining power, and weighted values are more appropriate.
    The results in this paper is intended to be used as a tool-kit for embedding bargaining outcomes into more complex models.
\end{abstract}

@@

Using cooperative game theory to model bargaining outcomes in a tractable way has quite a few examples in the industrial organization literature.
The case of one indispensable player and a large number of small ones is particularly important, for example, in the context of vertical markets or platforms.
